Formal Paper Draft

### 2022-01-12 PaperDraft.Rmd
updates to files

```{r, echo = FALSE}
mds1 <- readRDS("2021-10-16_simulation1_mds_list.RDS")
tsne1 <- readRDS("2021-10-16_simulation1_tsne_list.RDS")

@@

#mean detection rates
Category <- c("Correctly Identified Influential", "Correctly Non-Identified Non-Influential")
TSNE <- c(round(mean(ci1),3), round(mean(cni1),3))
MDS <- c(round(mean(ci2),3), round(mean(cni2),3))
Isomap <- c("","")
Sammon <- c("","")
temp <-rbind(TSNE, MDS, Isomap, Sammon)
colnames(temp) <- Category
kable(temp)

@@

$$D^2 = (\vec{x} - \mu)^t \Sigma^{-1} (\vec{x} - \mu) $$
The mahalanobis distance can be calculated across each of the simulated datasets and compared to get a sense for how the efficacy of the PERMANOVA-based method changes when influential points are only mildly outlying compared to very extreme points. *Ideally, we would see detection rates that are substantively larger when assessing influential points that have a larger mahalanobis distance than those that have a smaller mahalanobis distance.  This allows for us to assess a power curve to determine how the method is able to detect differences of different magnitudes. *

>>>>

```{r, echo = FALSE}
#mds1 <- readRDS("2021-10-16_simulation1_mds_list.RDS")
mds1 <- readRDS("2022-01-12_simulation1_mds_list.RDS")
tsne1 <- readRDS("2021-10-16_simulation1_tsne_list.RDS")
sammon1 <- readRDS("2022-01-12_simulation1_Sammon_list.RDS")

@@

#sammon
ci3 <- sapply(df4list, correctInfluence)
cni3 <- sapply(df4list, correctNonInfluence)

#mean detection rates
Category <- c("Correctly Identified Influential", "Correctly Non-Identified Non-Influential")
TSNE <- c(round(mean(ci1),3), round(mean(cni1),3))
MDS <- c(round(mean(ci2),3), round(mean(cni2),3))
Isomap <- c("","")
Sammon <- c(round(mean(ci3),3), round(mean(cni3),3))
temp <-rbind(TSNE, MDS, Isomap, Sammon)
colnames(temp) <- Category
kable(temp)

@@

$$D^2 = (\vec{x} - \mu)^t \Sigma^{-1} (\vec{x} - \mu) $$
The mahalanobis distance can be calculated across each of the simulated datasets and compared to get a sense for how the efficacy of the PERMANOVA-based method changes when influential points are only mildly outlying compared to very extreme points. *Ideally, we would see detection rates that are substantively larger when assessing influential points that have a larger mahalanobis distance than those that have a smaller Mahalanobis distance.  This allows for us to assess a power curve to determine how the method is able to detect differences of different magnitudes. *
